Expert-In-The-Loop Causal Discovery: \\ Iterative Model Refinement Using Expert Knowledge

### 2025-02-10 paper/main.tex
Make equations compacter

\begin{equation}
	\begin{split}
		x &= \textrm{rand}([0, 1]) \\
		\mathrm{Expert}(\alpha) &= \begin{cases} 
			\mathrm{TrueReln}(X, Y),  & \textrm{if  } x <= \alpha \\
			\textrm{rand}(X \rightarrow Y, Y \leftarrow X, \textrm{None}) & \textrm{otherwise} \\
				\end{cases} \\
	\end{split}
\end{equation}

where given the true DAG, $ G $:

\begin{equation}
	\begin{split}
	\mathrm{TrueReln}(X, Y) &= \begin{cases}
					X \rightarrow Y, & \textrm{if } X \rightarrow Y \in G \\
					Y \rightarrow X, & \textrm{if } Y \rightarrow X \in G \\
					\textrm{None}, & \textrm{otherwise }
				  \end{cases}
	\end{split}
\end{equation}

An important point to note here is that the effective accuracy of $
\mathrm{Expert} $ is higher than $ \alpha $ as even when giving a random
answer, there is a $ 1 $ in $ 3 $ chance that the answer is correct. Therefore,
an $ \mathrm{Expert} $ with accuracy $ \alpha $, has an effective accuracy:

\begin{equation}
	\alpha_{\mathrm{eff}} = \alpha + (1 - \alpha) / 3
\end{equation}

@@

, we use the
\textsc{RankedExpand} method together with a version of the strong ancestral
oracle that can make mistakes.

>>>>

\begin{equation}
	\begin{split}
		x &= \textrm{rand}([0, 1]) \\
		\mathrm{Expert}(\alpha) &= \begin{cases} 
			\mathrm{TrueReln}(X, Y),  & \textrm{if  } x <= \alpha \\
			\textrm{rand}(X \rightarrow Y, Y \leftarrow X, \textrm{None}) & \textrm{otherwise} \\
				\end{cases} \\
		\mathrm{TrueReln}(X, Y) &= \begin{cases}
				X \rightarrow Y, & \textrm{if } X \rightarrow Y \in G_{\textrm{true}} \\
				Y \rightarrow X, & \textrm{if } Y \rightarrow X \in G_{\textrm{true}} \\
					\textrm{None}, & \textrm{otherwise }
				  \end{cases}
	\end{split}
\end{equation}

where $G_{\textrm{true}}$ is the true data generating DAG.

An important point to note here is that the effective accuracy of $
\mathrm{Expert} $ is higher than $ \alpha $ as even when giving a random
answer, there is a $ 1 $ in $ 3 $ chance that the answer is correct. Therefore,
an $ \mathrm{Expert} $ with accuracy $ \alpha $, has an effective accuracy, $ \alpha_{\mathrm{eff}} = \alpha + (1 - \alpha) / 3 $.

@@
